Three 40 to 50 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-04-05 papers/ms.tex
update ms

\title{
  Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of how stellar clusters evolve.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the latter three systems, which are in other
  sub-components of the complex (RSG-5 and CH-2).
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 (in RSG-5) is
  $46^{+9}_{-7}$\,Myr old, while KOI-7368 and KOI-7913 (in CH-2) are
  $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, they are
  all most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $4\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets are therefore the first empirical
  demonstration that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest (KOIs)
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we discuss the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of implications for the size-evolution of close-in
mini-Neptunes (Section~\ref{sec:disc_conc}).

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The stellar groups near KOI-7368, KOI-7913, and Kepler-1643
    are $\approx$40 million years old.} 
    {\it Top row}: 
    Color-absolute magnitude diagram of candidate Cep-Her members, in
    addition to candidate members of the $\delta$~Lyr~cluster
    ($\approx38$\,Myr; \citealt{bouma_kep1627_2022}) and and the Gaia
    EDR3 Catalog of Nearby Stars (gray background).  The left and
    right columns shows stars in RSG-5 and CH-2, respectively.  The
    range of colors is truncated to emphasize the pre-main-sequence.
    {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.
    The detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present for the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep{kiman_calibration_2021}.  At $\approx$M0V, if
the secondary were in older than $\approx 500\,{\rm Myr}$, it would be
more common for its H$\alpha$ component to be observed in absorption
\citep[][Figure~4]{kiman_calibration_2021}.  H$\alpha$ emission in
late K-dwarfs is rarer still. Based on the data from K.~Rocio et al's
analysis\footnote{Available at
\url{https://zenodo.org/record/4659293#.YkuKh27MKDV}}, a $\approx$K6V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.

@@

\section{Discussion \& Conclusions}
\label{sec:disc_conc}

@@

>>>>

\title{
  Three 40 to 50 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of open cluster dispersal.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the latter three systems, which are in other
  sub-components of the complex (RSG-5 and CH-2).
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 (in RSG-5) is
  $46^{+9}_{-7}$\,Myr old, while KOI-7368 and KOI-7913 (in CH-2) are
  $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, they are
  all most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $4\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets therefore empirically
  demonstrate that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest (KOIs)
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  
We conclude with a few caveats, 
and discuss implications for the size-evolution of close-in
mini-Neptunes (Section~\ref{sec:disc_conc}).

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The stellar groups near KOI-7368, KOI-7913, and Kepler-1643
    are 40 to 50 million years old.} 
    {\it Top row}: 
    Color-absolute magnitude diagram of candidate Cep-Her members, in
    addition to candidate members of the $\delta$~Lyr~cluster
    ($\approx38$\,Myr; \citealt{bouma_kep1627_2022}) and and the Gaia
    EDR3 Catalog of Nearby Stars (gray background).  The left and
    right columns shows stars in RSG-5 and CH-2, respectively.  The
    range of colors is truncated to emphasize the pre-main-sequence.
    {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.
    The detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present in the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep{kiman_calibration_2021}.  At $\approx$M0V, if
the secondary were in older than $\approx 500\,{\rm Myr}$, it would be
more common for its H$\alpha$ component to be observed in absorption
\citep[][Figure~4]{kiman_calibration_2021}.  H$\alpha$ emission in
late K-dwarfs is rarer still. Based on the data from K.~Rocio et al's
analysis\footnote{Available at
\url{https://zenodo.org/record/4659293\#.YkuKh27MKDV}}, a $\approx$K6V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.

@@

\section{Discussion \& Conclusion}
\label{sec:disc_conc}

@@

\subsection{Normal-Sized Mini-Neptunes Exist at 40$\,$Myr}

Perhaps the most significant point about
Kepler-1643~b, KOI-7368.01, and KOI-7913 is that they have normal
sizes.
{\bf TODO for LGB: write more about this}

\subsection{Summary}

We have argued that Kepler-1643~b, KOI-7368.01, and KOI-7913 {\it i)}
are all $\approx$40 million years old, and {\it ii)} that each signal
is most likely planetary.  The evidence for the planetary
interpretation comes from an application of \texttt{VESPA} to the
Kepler data, alongside new adaptive optics imaging from NIRC2.  The
validity of the \texttt{VESPA} framework rests on the premise that
non-astrophysical false positives, including false alarms and known
neighboring eclipsing binaries, can be rejected.  Kepler-1643 and
KOI-7368 both pass all but one of the canonical vetting checks: the
check for centroid offsets between the in and out-of-transit phases.
For both cases, we have argued the weak observed shifts are most
likely caused by starspot-induced variability in specific quarters
shifting the stellar center-of-light.

Each system has multiple indicators of youth that support their
reported ages.  For Kepler-1643, perhaps the strongest youth indicator
is its physical and kinematic association with RSG-5.  Based on the
color-absolute magnitude diagram, we seem to be able to select members
of this cluster with a false positive rate of $\ll 5\%$
(Figure~\ref{fig:age}), and Kepler-1643 is one such member.  Its
rotation period period agrees with this assessment, and {\bf its
lithium is a little low}.

The spatial and kinematic arguments for the youth of KOI-7368 and
KOI-7913 are necessarily weaker because they are in an association of
stars, CH-2, that is much more tenuous.  For KOI-7913 this is not of
particular concern, since it happens to be a binary.  Both components
have isochronal ages consistent with $40$\,Myr, but the measurement
for the secondary is more constraining since it is less massive.  Both
components also show H$\alpha$ in emission, which for the $\approx$K6V
primary is a good indicator that the star is $\lesssim$100$\,$Myr old.
For KOI-7368, which is slightly more massive, the Li 6708\AA\ EW
measurement and stellar rotation period are more constraining, and
provide independent verification of the stellar youth.
